A method for inference of fundamental stellar parameters using high resolution spectra

### 2014-01-16 paper/paper.tex
updated all the configs

\paragraph{SPC} A very popular method behind the Kepler follow-up program is Stellar Parameter Classification (SPC) \citep{blj+12}). This compares high resolution optical echelle spectra ($R \sim$ 45,000) to high resolution synthetic grids computed with Kurucz models by a cross-correlation method. The best fit parameters and uncertainties are calculated by the relative values of the cross-correlation coefficient. It is uncertain how statistically justified this uncertainty estimate is. While this is a pixel-to-pixel method, it uses only a small region of the optical spectrum ($5000 - 5300$\AA) where the spectral library has been carefully tweaked\footnote{changes to line centers and $\log(gf)$ values were on the table} to match  high resolution models of the Sun and Vega.

\paragraph{General trends}
Successful pixel-to-pixel methods that are successful mask spectra lines if they are doing a full spectrum fit (although this brings up the concern of \citet{mga13}). Techniques which do not mask or just use a $\chi^2$ function are limited to a small region of the spectrum where presumably their stellar models are \emph{good enough}.
By limiting themselves to These areas can use intense scrutiny from a spectral modeller to guarantee that the models match reality.

>>>>

\paragraph{SPC} A very popular method behind the Kepler follow-up program is Stellar Parameter Classification (SPC) \citep{blj+12}). This compares high resolution optical echelle spectra ($R \sim$ 45,000) to high resolution synthetic grids computed with Kurucz models by a cross-correlation method. The best fit parameters and uncertainties are calculated by the relative values of the cross-correlation coefficient. It is uncertain how statistically justified this uncertainty estimate is. Currently SPC uses only a small region of the optical spectrum ($5000 - 5300$\AA) where the spectral library has been carefully tweaked\footnote{changes to line centers and $\log(gf)$ values were on the table} to match high resolution models of the Sun and Vega.

\paragraph{General trends}
Successful pixel-to-pixel methods either mask bad spectral lines or limit themselves to a narrow region of the spectrum, where they can be relatively certain that the spectral library does not contain gross systematical errors. This implicit masking brings up similar concerns to those of \citet{mga13}: how do you know that you are fitting the region of the spectrum that contains the most information about the stellar properties?
